FancyMc Moves \\ Fusion Moves for Multicut Objectives

### 2014-09-29 paper/egpaper_for_review.tex
improved paper

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
%for tikz
\usepackage{tikz,pgfplots}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}

@@

\subsubsection{Solver for the Multicut Objective}
   \begin{itemize}
   \item Multicut~\cite{kappes_2011_emmcvpr}
   \item Expand and Explorer~\cite{bagon_2011_arxiv}
   \item Fast Planar CC~\cite{yarkony_2012_eccv}
   \item Break and Conquer \cite{alush_2013_simbad}.
   \item Cut Glue And Cut~\cite{beier_2014_cvpr}
   \end{itemize}

@@

@@

>>>>

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}

\newtheorem{theorem}{Theorem}

@@

\subsubsection{Solver for the Multicut Objective}

    \input{inputs/tab_mc_overview.tex}

   \begin{itemize}
   \item Multicut~\cite{kappes_2011_emmcvpr}
   \item Expand and Explorer~\cite{bagon_2011_arxiv}
   \item Fast Planar CC~\cite{yarkony_2012_eccv}
   \item Break and Conquer \cite{alush_2013_simbad}.
   \item Cut Glue And Cut~\cite{beier_2014_cvpr}
   \end{itemize}

@@

\begin{theorem}[NameMe]
Solving ??? on the contracted graph is 
equivalent to solving ??? on the 
original graph with additional 
must link constraints
\end{theorem}

\begin{proof}[Proof of theorem ]
todo
\end{proof}

\begin{theorem}[NameMe]
Solving ??? and ??? will never increase the best energy...
\end{theorem}

\begin{proof}[Proof of theorem ]
todo
\end{proof}

\begin{theorem}[NameMe]
If the all cut edges of the global optimal
solution are included in the union of
the cut edges of two proposals, solving
??? will find the global optimal solution
\end{theorem}

\begin{proof}[Proof of of theorem]
todo
\end{proof}

@@

\begin{algorithm}
\begin{scriptsize}
\caption{Fusion Based Algorithms}\label{alg:fusion}
\begin{algorithmic}[1]
\Procedure{Intersection-Based-Inference}{GEN,$J$,$X$}
\State $x^0 \gets \textrm{initial state form } X$
\State $n \gets 0 $                                 \Comment{Number of moves}
\State $m \gets 0 $                                 \Comment{Number of moves without progress}
\While{$m < m_{\max}$ and $n < n_{\max}$ }
\State $n \gets n+1$ 
 \State $x'\gets GEN(x^{n-1},J,X)$                    \Comment{Generate proposal}
 \If{$J(x^{n-1}) \leq J(x')$}                       
   \State $x^{n} \gets Fuse(x^{n-1},x',J)$             
 \Else
   \State $x^{n} \gets Fuse(x',x^{n-1},J)$
 \EndIf
 \If{$J(x^{n}) \leq J(x^{n-1})$}
   \State $m \gets 0$                                 \Comment{Reset counter}
 \Else
   \State $m \gets m+1$                               \Comment{Increment counter}
 \EndIf
\EndWhile
\State \textbf{return} $x^n$
\EndProcedure
\end{algorithmic}
\end{scriptsize}
\end{algorithm}

\begin{algorithm}
\begin{scriptsize}
\caption{Fusion Moves}\label{alg:fusion_moves}
\scriptsize
\begin{algorithmic}[1]
\Require $J(x) \leq J(x')$
\Ensure $J(\hat{x}) \leq J(x)$
\vspace{0.2cm}
\Procedure{Fuse}{$x,x',J$}
\State $\bar{x} \gets \textbf{\scriptsize{Intersect}}(x,x')$  
    \Comment{
        \begin{minipage}{0.4\linewidth} 
            \begin{tiny}
            \begin{singlespace}
                intersect
                uncut edges in $x$ and $x'$,
                return  
                connected component labeling
            \end{singlespace}
            \end{tiny}
        \end{minipage}
    }
\vspace{0.1cm}
\State $ \tilde{G}=(\tilde{E},\tilde{V}),\tilde{W} 
    \gets \textbf{\scriptsize{Contract}}(G,W,\bar{x})$  
    \Comment{ 
        \begin{minipage}{0.2\linewidth} 
            \begin{tiny}
            \begin{singlespace}
                Contract all edges 
                which are uncut in $\bar{x}$ 
            \end{singlespace}
            \end{tiny}
        \end{minipage}
    }
\vspace{0.1cm}
\State $\tilde{x}^*= \argmin\limits_{\tilde{x}} \sum\limits_{e_{ij} \in \tilde{E}} \tilde{w}_{ij}[\tilde{x}_i \neq \tilde{x}_j]$
    \Comment{ 
        \begin{minipage}{0.3\linewidth} 
            \begin{tiny}
            \begin{singlespace}
                Solve the multicut objective
                on smaller graph $\tilde{G}=(\tilde{V},\tilde{E})$
            \end{singlespace}
            \end{tiny}
        \end{minipage}
    }

\State $\hat{x} \gets \textbf{\scriptsize{ProjectBack}}(\tilde{x}^*)$
    \Comment{ 
        \begin{minipage}[\textheight]{0.4\linewidth} 
            \begin{tiny}
            \begin{singlespace}
                Translate the connected component
                labeling $\tilde{x}^*$ of $\tilde{G}$ 
                to a connected component labeling of $G$
            \end{singlespace}
            \end{tiny}
        \end{minipage}
    }
\State \textbf{return} $\hat{x}$
\EndProcedure
\vspace{0.3cm}
\Procedure{FUSE$_{\textrm{BASE}}$}{$x,x',J$}
\State \textbf{return} ${\arg\min}_{\bar{x} \in \{x,x'\}}J(\bar{x})$
\EndProcedure
\end{algorithmic}
\end{scriptsize}
\end{algorithm}

\begin{algorithm}
    \begin{scriptsize}
        \caption{Proposal Generators}\label{alg:proposal_gen}   
        \begin{algorithmic}[1]
            %\Require $J(x) \leq J(x')$
            %\Ensure $J(\hat{x}) \leq J(x)$
            %\vspace{0.3cm}
            \Procedure{Rand2Coloring}{$x,G=(E,V),W$}
            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
            \State $x'= \argmin\limits_{\bar{x}} \sum\limits_{e_{ij} \in E } \tilde{w}_{ij}[\bar{x}_i \neq \bar{x}_j]  [x_i = x_j]   $

            $ \quad\quad s.t.\quad x_i \in \{0, 1\} \forall i $
            \State \textbf{return} $x'$
            \EndProcedure
            %
            %
            \vspace{0.3cm}
            \Procedure{RandEdgeWeightedWatersheds}{$x,G=(E,V),W$}
            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
            \State $ getRandomSeeds$
            \State $ runEdgeWeightedWs$
            \EndProcedure   
            %
            %
            \vspace{0.3cm}
            \Procedure{RandHierarchicalClustering}{$x,G=(E,V),W$}
            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
            \State $\hat{G}=(\hat{E},\hat{V}) \gets G=(E,V)$
            \State $\hat{W} \gets W$
            \While{$|\hat{V}|>\gamma$ \textbf{and}  $\max(\hat{W})>\theta$ }
                \State $\hat{G}=(\hat{E},\hat{V}),\hat{W} \gets 
                    \textbf{\scriptsize{contract}}(\hat{G},\hat{W},  \argmax\limits_{\hat{E}}(\hat{W}) )$
            \EndWhile
            \State $x' \gets \textbf{\scriptsize{getClusterResults}}(???) $ 
            \EndProcedure
        \end{algorithmic}
    \end{scriptsize}
\end{algorithm}
